Dark matter halo shape at $z=0$ in the Auriga simulations: radial evolution and alignment with the stellar disk

### 2019-07-19 Document/paper.tex
edit

>>>>

We also found that the alignment betwen the stellar disk and dark
matter halo changes with the radius.
At a radius of $0.25R_{200}$ the alignment is almost perfect and
degrades at smaller and larger distances.
This alignment evolution implies a radial twisting between the ellipsoids
describing the halo shape. 
We quantify this twist with the standard deviation of the angle
between the two minor axis at radii below $\leq 0.5R_{200}$ and find
that it strongly correlates is with the disk size and the core gas
mass density, there is only a weak correlation with the stellar mass
in the disk.
